The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-12-05 paper/ms.tex
vsa references

One of the primary ways to determine, in a chemical sense, whether the stars in our sample are drawn from the Galactic disk(s), bulge or halo, is with the ratio of their $\alpha$-elements to Fe. The $\alpha$ elements are formed after He burning (e.g. Mg, Ti, Si, Ca) and largely dispersed into the interstellar medium through Type~II supernovae (SNII) \citep{Matteucci2001}. It has been shown by many studies \citep[e.g.][and references therein]{Edvardsson1993, Adibekyan2012, Feltzing2013, Bensby2014}, that the Galactic thick and thin disks separate in the $\alpha$ elements, where the thick disk is enhanced in [Mg, Si, Ca, Ti/Fe] compared to the Galactic thin disk at a given metallicity. In Fig.~\ref{alphael}, we display the [Mg/Fe] abundance ratio as a function of [Fe/H] for our stars (black circles), compared\footnote{There may to be systematics between our [X/Fe] abundance scale and those of our comparison samples.} to representative thick and thin disk stars from \cite[open red squares]{Bensby2014} and \cite[open orange triangles]{Adibekyan2012}.

>>>>

One of the primary ways to determine, in a chemical sense, whether the stars in our sample are drawn from the Galactic disk(s), bulge or halo, is with the ratio of their $\alpha$-elements to Fe. The $\alpha$ elements are formed after He burning (e.g. Mg, Ti, Si, Ca) and largely dispersed into the interstellar medium through Type~II supernovae (SNII) \citep{Matteucci2001}. %It has been shown by many studies \citep[e.g.][and references therein]{Edvardsson1993, Adibekyan2012, Feltzing2013, Bensby2014}, that the Galactic thick and thin disks separate in the $\alpha$ elements, where the thick disk is enhanced in [Mg, Si, Ca, Ti/Fe] compared to the Galactic thin disk at a given metallicity. 
The Galactic disk can be chemically dissected into a low- and a high-alpha component that have different vertical and age structure \citep[see e.g.][]{2016ApJ...823...30B,2017A&A...608L...1H,2018MNRAS.475.5487S}, and are commonly associated with the thin and the thick disk \citep[e.g.][and references therein]{Edvardsson1993, Adibekyan2012, Feltzing2013, Bensby2014}. At a given metallicity, the thick disk is enhanced in [Mg, Si, Ca, Ti/Fe] compared to the Galactic thin disk.

In Fig.~\ref{alphael}, we display the [Mg/Fe] abundance ratio as a function of [Fe/H] for our stars (black circles), compared\footnote{There may to be systematics between our [X/Fe] abundance scale and those of our comparison samples.} to representative thick and thin disk stars from \cite[open red squares]{Bensby2014} and \cite[open orange triangles]{Adibekyan2012}.
